\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue, roman]{casual}
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Baosheng}
\familyname{Wang}
\title{Curriculum Vitae}
\mobile{+86 18721962910}
\email{wilson\_91@foxmail.com}


\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


\begin{document}
\maketitle

\section{Education}
\cventry{Sep 2013 -- Mar 2016}{MS in Computer Vision}{Tongji University}{Shanghai, China}{Supervisor: Weidong Zhao}{}
\cventry{Sep 2009 -- Jun 2013}{BA in Computer Science and Technology}{Lanzhou Jiaotong University}{Lanzhou, China}{Rank: 1st}{}

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}



\section{Work Experience}
\cventry{Mar 2016 -- Present}{Senior Applied Scientist}{Microsoft}{China}{Bing Metrics Team}
{\begin{itemize}
    \item Leveraging SOTA ML/DL/LLM algorithms to build and optimize core product features.
    \item Led a team to architect and build an offline evaluation pipeline from scratch by fine-tuning open-source LLMs (e.g., Qwen), achieving quality parity with human crowd judges. The system serves hundreds of developers and has generated millions of dollars in cost savings.
    \item Spearheading the development of next-generation offline evaluation metrics utilizing advanced LLMs (e.g., GPT-5) to supersede legacy systems.
\end{itemize}}

\cventry{Jun 2015 -- Sep 2015}{Software Engineer Intern}{Microsoft}{China}{Bing Satori Team}
{Developed web data extraction pipelines and analysis tools for Satori, a core data processing team within the Bing search center. Utilized C\#, Web API, and SCOPE.}

\cventry{Jan 2015 -- Mar 2015}{Algorithm Intern}{HiScene}{China}{Algorithm Team}
{Co-designed and implemented image processing algorithms for mobile applications using C++ and OpenCV. Led the implementation of an OCR demo.}



\section{Honors \& Awards}
\cventry{2013}{Selected for Graduate Admission Waiver (Top 5\%)}{Tongji University}{}{}{}
\cventry{2012}{WanQiaoStar Scholarship, Second Prize Scholarship}{}{}{}{}
\cventry{2009--2011}{National Encouragement Scholarship, First Prize Scholarship}{}{}{}{}

\section{Skills}
\cventry{Programming}{Python, C\#, C++, C, SCOPE}{}{}{}{}
\cventry{ML Frameworks}{PyTorch, Hugging Face, LLMs}{}{}{}{}
\cventry{Tools \& Cloud}{Azure, Cosmos, Git, OpenCV, LaTeX}{}{}{}{}
\cventry{Languages}{English (Fluent), Chinese (Native)}{}{}{}{}

\section{Community}
\cventry{Blog}{\url{https://king1991wbs.github.io/wilson}}{}{}{}{}
\cventry{Stack Overflow}{\url{https://stackoverflow.com/users/3322579/wilson}}{}{}{}{}
\cventry{GitHub}{\url{https://github.com/king1991wbs}}{}{}{}{}

%\section{Hobbies}
%\cvitem{Sports:}{Jogging,Small Ball(Badminton,PingPang etc.)}
%\cvitem{Life:}{Enjoy eating,want to be good at cooking}
%\cvitem{Part time}{music,movie,reading,pencil sketch}
% \closesection{}                   % needed to renewcommands
% \renewcommand{\listitemsymbol}{-} % change the symbol for lists


\end{document}
